\section{Work and Research Experience}

\outerlist{

\entry{\textbf{Graduate Researcher}, Trottier Space Institute, McGill University \hfill \textit{Sept 2023 -- Present}}
\innerlist{
  \entry{Developed and maintained pipelines for CHIME/FRB to process 4500+ events with reproducible fluence and sensitivity calculations.}
  \entry{Refactored legacy code for GitHub Actions and Docker deployment; integrated into the collaboration's workflow system.}
  \entry{Added support for baseband and VLBI data; pipeline now underpins multiple CHIME/FRB analyses.}
}

\entry{\textbf{Machine Learning Intern}, Trottier Institute for Research on Exoplanets (iREx) \hfill \textit{May -- Aug 2023}}
\innerlist{
  \entry{Modeled exoplanet populations using KDE and Normalizing Flows; merged NASA and MOCA datasets to estimate system ages.
}
  \entry{Built an MCMC pipeline to compute stellar proper motions from WISE and Pan-STARRS data.}
}

\entry{\textbf{Undergraduate Researcher}, McMaster University \hfill \textit{Sept 2021 -- Apr 2023}}
\innerlist{
  \entry{Analyzed CO isotopologues in galaxy mergers using 3-D ALMA data cubes to study gas properties.}
  \entry{Built C++ solvers for fast oscillating integrals using Picard-Lefschetz theory for application in physics.}
  \entry{Cross-matched SDSS, GALEX, and MPA-JHU catalogs and ran phase-space analysis on 100,000 galaxies to study star formation and quenching processes.}
}
}

\section{Leadership \& Engagement}

\outerlist{
  \entry{\textbf{Community Advisor}, McMaster University \hfill \textit{2021 -- 2023} \\
  Supported 100+ students in residence through conflict resolution, emergency response, and event programming.}

  \entry{\textbf{VP, Professional Development}, McGill Physics Grad Association \hfill \textit{2023 -- 2024} \\
  Organized career panels, workshops, and alumni networking to support graduate student development.}

  \entry{\textbf{Peer Leader}, Student Success Centre, McMaster University \hfill \textit{2021 -- 2022} \\
  Led outreach and professional development events for international students, including webinars and resource creation.}
}